The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-12 src/ms.tex
slightly reorganize end sections

\subsection{Roadmap}

\secauthor{Clara Brasseur}

The Astropy Roadmap\footnote{\url{https://github.com/astropy/astropy-project/blob/main/roadmap/roadmap.md}} is a document in the astropy-project repository that captures high level actionable items that the Astropy project aims to undertake to improve the health and stability of the  project. It is a static document that is revisited regularly at the Astropy coordination meetings, to keep track of progress and write new versions as needed. There is a related project board linked to the Roadmap document, that holds specific issues and efforts related to Roadmap items. The project board is a living document that is continually updated as work is planned, assigned, and completed.

All items in the Roadmap have been agreed to be priorities for the Astropy Project, and are color-coded based on resources (both time/effort and developers/expertise) needed to complete the item. Green items are well underway, have sufficient resources/support and a plan in place for completion. Orange items are well defined, and work for aquiring sufficient resources underway. Red items do not yet have a plan for implementation and need more resources.
\todo{addition}{Add some examples of high priority items from the roadmap in a new paragraph here}
The Astropy Roadmap originates from the March 2021 Astropy Coordination meeting where it was first drafted before being handed off to a newly formed Astropy Roadmap working group for completion. The Roadmap in its currant form was adopted via pull request in December 2021.

\section{Learn Astropy} \label{sec:learn}

@@

@@

\section{Community Engagement}

>>>>

\subsection{Learn Astropy} \label{sec:learn}

@@

\subsection{A roadmap for future priorities}
% \secauthor{Clara Brasseur}

The
\href{https://github.com/astropy/astropy-project/blob/main/roadmap/roadmap.md}{Astropy Roadmap} is a document in the \texttt{astropy-project} \github
repository within the \astropy organization that captures high level actionable
items that the Astropy project aims to undertake to improve the health and
stability of the project. It is a static document that is revisited regularly at
the Astropy coordination meetings, intended to keep track of progress and write
new versions as needed. There is a related project board linked to the Roadmap
document that holds specific issues and efforts related to Roadmap items. The
project board is a living document that is continually updated as work is
planned, assigned, and completed.

All items in the Roadmap have been agreed to be priorities for the Astropy
Project, and are color-coded based on resources (both time/effort and
developers/expertise) needed to complete the item. Green items are well
underway, have sufficient resources/support and a plan in place for completion;
For example, efforts to improve the discoverability of documentation and
educational materials by overhauling the Learn website, which is underway (see
Section~\ref{sec:learn}).
Orange items are well defined, and work for acquiring sufficient resources
underway; For example, the goal of providing next-generation spectroscopic
reduction, analysis, and visualization tools usable by individual researchers
and larger surveys.
Red items do not yet have a plan for implementation and need more resources; For
example, the goal of improving interoperability with performant I/O file formats
and libraries such as HDF5 and Dask.
The Astropy Roadmap originates from the March 2021 Astropy Coordination meeting
where it was first drafted before being handed off to a newly formed Astropy
Roadmap working group for completion. The Roadmap in its current form was
adopted via pull request in December 2021.

@@

Community Engagement
